\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Planing for project}
\author{Olov Rahm}
\date{January 2025}

\begin{document}

\maketitle
\section{From Intro}
\noindent
(i) Explotre and preprocess data
\\
(ii) try some or all classification methods, which are these?
\begin{itemize}
    \item Logistic Regression
    \item Discriminant analysis: LDA, QDA
    \item K-nearest neighbor
    \item Tree-based methods: classification trees, random forests, bagging
    \item Boositing
\end{itemize}
(iii) Which of these are to be "put in producion"?

\section{From Data analysis task}
\begin{itemize}
    \item Can any trend be seen comparing different hours, weeks, months?
    \item Is there any diffrence between weekdays and holidays?
    \item Is there any trend depending on the weather?
\end{itemize}

\section{From Implementation of methods}

Each group member should implement one family each, who did what shall be clear!
\\
DNNs are encouraged to be implemented, do this if there is time. 
(DNN is not a thing a group member can claim as their family.)
\\
Implement a naive version, let's do: $\textit{Always low\_bike\_demand}$
\subsection{What to do with each method}
\begin{enumerate}
    \item Implement the method (each person individually)
    \item Tune hyper-parameters, discuss how this is done (each person individually)
    \item Evaluate with for example cross-validation. Don't use $E_{k-fold}$ (what is that?) (need to do together)
    \item (optional) Think about input features, are all relevant? (together)
\end{enumerate}

\noindent
Before training, unify pre-processing FOR ALL METHODS and choose ONE OR MULTIPLE metrics to evaluate the model.
(is it neccesary to have the same for all?, is it beneficial?) Examples:
\begin{itemize}
    \item accuracy
    \item f1-score
    \item recall
    \item precision
\end{itemize}

\noindent
Use same test-train split for ALL MODELS

\end{document}
